Road Segment Prioritization for Bicycle Infrastructure

### 2021-02-07 README.Rmd
text edits - potential demand

Relying only on existing cycling activity to prioritise cycling
infrastructure can reinforce existing cycling patterns and ignores
potential cycling demand that could be satisfied by a connected network.
To avoid this issue, @duthie2014optimization choose to ignore existing
demand completely, and focus on creating a network that connects the
entire study area. @olmos2020data obtain the distance distribution of
cyclists using a smartphone-based bicycle GPS data, and then use a
rejection-sampling algorithm on the OD data of the study area to match
the potential demand distribution to the distribution obtained from GPS
data.

*Origin-Destination (OD)* data can be obtained from a range of sources,
including GPS data, household travels surveys and Census data on work
locations. In areas where observed OD data is unavailable, modelling
techniques such as spatial interaction models can be used to estimate
travel volumes between zones [@black1995spatial; @martinez2013new;
@wilson1971family]. In this paper we use open access data from the UK
census [@ONS2011flowdata], which contains aggregate statistics on
number of commuters between administrative zones --- Middle layer Super
Output Areas (MSOA) --- by mode of travel. MSOAs have an average
population of just over 8000 [@ofn2018population].^[ See
<https://wicid.ukdataservice.ac.uk/> for open access to the OD data.]
Figures \@ref(fig:potdemhistograms) and \@ref(fig:desirefacetcycling)
illustrates the proportion of trips cycled by distance and the
geographic extent of the input OD dataset used in this paper.

>>>>

Many of the cycling network studies mentioned above use demand data for cycling as a starting point. 
Some use existing cycling demand, some calculate potential cycling demand, and others ignore demand completely. 
@duthie2014optimization note that relying only on existing cycling activity to prioritise cycling
infrastructure can reinforce existing cycling patterns and ignores potential cycling demand that could be satisfied by a connected network.
To avoid this issue they choose to ignore existing demand completely, and focus on creating a network that connects the
entire study area. 
@olmos2020data opt to calculate potential demand instead; they obtain the distance distribution of cyclists using a smartphone-based bicycle GPS data, and then use a rejection-sampling algorithm on the OD data of the study area to match
the potential demand distribution to the distribution obtained from GPS data.

*OD* data can be obtained from a range of sources,
including GPS data, household travels surveys and Census data on work
locations. In areas where observed OD data is unavailable, modelling
techniques such as spatial interaction models can be used to estimate
travel volumes between zones [@black1995spatial; @martinez2013new;
@wilson1971family]. In this paper we use open access data from the UK
census [@ONS2011flowdata], which contains aggregate statistics on
number of commuters between administrative zones --- Middle layer Super
Output Areas (MSOA) --- by mode of travel. MSOAs have an average
population of just over 8000 [@ofn2018population].^[ See
<https://wicid.ukdataservice.ac.uk/> for open access to the OD data.]
Figures \@ref(fig:potdemhistograms) and \@ref(fig:desirefacetcycling)
illustrates the proportion of trips cycled by distance and the
geographic extent of the input OD dataset used in this paper.
